\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/eval.tex
working on s6

\section{Evaluation}
\label{sec:eval}
We evaluate \tool for the problem of {\it secure prediction}, where a server has a machine learning model, a client has an input, and after the protocol execution the client learns a label on his input.
From the protocol execution, the server learns nothing about the client's input and the client learns nothing about the server's model beyond what is revealed from the computed label.
This setting has been previously studied in~\cite{shafindss,minionn}
We first implement benchmarks of ~\cite{shafindss} and~\cite{minionn} in \tool to compare against 
previous work.
Next, we demonstrate the generality of \tool by implementing state-of-the-art machine learning models.
Finally, we discuss a model that requires pipelinig.
Our results are in two settings, a LAN setting and a cross-continent WAN setting.
The round trip time for two machines in a LAN setting is 1ms and in WAN setting is 40ms.
Each machine has a Intel(R) Xeon(R) CPU E5-2673 v3 processor running at 2.40GHz with
28 GBs of RAM. The \tool compiler is written in Python and compiles each of our benchmarks
in under a second to C++ code that makes calls to the ABY library~\cite{aby}.
We use an off-the-shelf solver (SeaHorn~\cite{seahorn}) to check the verification conditions
required to prove that the array indices remain in bound.
The solver takes less than a minute on our largest benchmark.
Since most of our benchmarks are related to machine learning, we set up some notation standard to machine learning and describe our benchmarks next.

@@

\noindent\textbf{Notation.} We use $[N]$ to denote $\{0,1,\dotsc, N-1\}$. 
Given a vector $x\in\R^d$, $\mathsf{argmax}\ x = i$ if $x(i) = \mathsf{max}\ \{x_1,\ldots,x_d\}$

In this paper, we focus on machine learning models for {\it classification}.
A {\it classifier} $C$ uses a trained {\it model} to {\it predict} a {\it label} $\ell$ for an input data point $x$. For example, given a data point which is a tuple of height and weight of an individual,
a classifier can predict a label ``male'' or ``female''. The {\it accuracy} of a classifier
refers to the fraction of data points that the classifier labels correctly from a given set of {\it test} data points.

@@

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
We evaluate \tool on the DNNs described in \minion~\cite{minionn} and the results are reported in Table~\ref{tab:nn}\footnote{\minion does not report the network round-trip time~\cite{minionn}.}.
Our goal here is to demonstrate that \tool
can provide performance competitive to specialized protocols for DNNs described in~\cite{secureml,cryptonets,minionn}. 
The first benchmark  is the DNN described in SecureML~\cite{secureml}.
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations (additions and multiplications)
except for the {\it argmax} at the end.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets} in \tool.
This DNN also uses square as the activation function and has one convolution (with 5 output channels) and one fully connected layer.
Finally, we compare against \minion on a CNN
with two convolutions (with 16 output channels each) and two fully connected layers.
In contrast to the previous two DNNs, this DNN uses ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using arithmetic gates but ReLU requires boolean-and gates.  For a complete description of these benchmarks and their accuracies,  the reader is referred to the original references.

@@

\subsection{Practical models}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of digits 0 to 9.
The first model that the tutorial describes is softmax regression
that provides an accuracy of 92\%. The classifier here evaluates
\[
 \mathsf{argmax}_{i} w_i^Tx+b_i
\]
Here, $i\in [10]$, $x$ is a 784 length vector obtained from the input image,
each $w_i$ is a 784 length vector, and each $b_i$ is a scalar. 
We implement this classifer in \tool and the results are shown in the first row of Table~\ref{tab:tf}.
Since, we are not familiar with any other tools that have used this model as a benchmark,
we only report execution time of \tool generated code.

>>>>

\section{Evaluation}
\label{sec:eval}
We evaluate \tool on the problem of {\it secure prediction}, where one
party (the server) has a machine learning model, and the other party
(the client) has an input. The goal is to compute the output of the
model on client's input, with the guarantee that the server
learns nothing about the input, and the client learns nothing
about the model beyond what is revealed from the output.

We first implement the benchmarks from Bost et al.~\cite{shafindss}
and \minion~\cite{minionn} (both of which study the same setting),
and show that the performance of the high-level code written in \tool
is comparable to their hand-crafted circuits
(Section~\ref{sec:shallow} and Section~\ref{sec:dnneval}).
%
Next, we demonstrate the generality and programmability aspects of
\tool by implementing state-of-the-art machine learning models from
Tensorflow~\cite{tensorflow} and \bonsai (\aseem{cite?}).
%
Finally, we
implement a Deep Neural Network (DNN) for CIFAR-10
dataset~\cite{cifar} from \minion~\cite{minionn} to illustrate the use
of partitioning in \tool.

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms resp. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM.
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Since most of our benchmarks
are related to machine learning, we set up some notation (largely
standard in machine learning) and describe our benchmarks next.

@@

\noindent\textbf{Notation.} We use $[N]$ to denote $\{0,1,\dotsc, N-1\}$. 
Given a vector $x\in\R^d$, $\mathsf{argmax}\ x = i$ if $x_i =
\mathsf{max}\ \{x_1,\ldots,x_d\}$.

We focus on the machine learning models for {\it classification}.
A {\it classifier} $C$ uses a trained {\it model} to {\it predict} a {\it label} $\ell$ for an input data point $x$. For example, given a data point which is a tuple of height and weight of an individual,
a classifier can predict a label ``male'' or ``female''. The {\it accuracy} of a classifier
refers to the fraction of data points that the classifier labels correctly from a given set of {\it test} data points.

@@

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
\label{sec:dnneval}
We evaluate \tool on the DNNs described in \minion~\cite{minionn} and the results are reported in Table~\ref{tab:nn}\footnote{\minion does not report the network round-trip time~\cite{minionn}.}.
Our goal here is to demonstrate that \tool
can provide performance competitive to specialized protocols for DNNs described in~\cite{secureml,cryptonets,minionn}. 
The first benchmark  is the DNN described in SecureML~\cite{secureml}.
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations (additions and multiplications)
except for the {\it argmax} at the end.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets} in \tool.
This DNN also uses square as the activation function and has one convolution (with 5 output channels) and one fully connected layer.
Finally, we compare against \minion on a CNN
with two convolutions (with 16 output channels each) and two fully connected layers.
In contrast to the previous two DNNs, this DNN uses ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using arithmetic gates but ReLU requires boolean-and gates.  For a complete description of these benchmarks and their accuracies,  the reader is referred to the original references.

@@

\subsection{Practical models}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of digits 0 to 9.
The first model that the tutorial describes is softmax regression
that provides an accuracy of 92\%. The classifier here evaluates
\[
 \mathsf{argmax}\ Wx+b
\]
Here, $i\in [10]$, $x$ is a 784 length vector obtained from the input image,
each $W$ is a $10\times 784$ matrix, and each $b$ is a $784$ length vector. 
We implement this classifer in \tool and the results are shown in the first row of Table~\ref{tab:tf}.
Since, we are not familiar with any other tools that have used this model as a benchmark,
we only report execution time of \tool generated code.
